More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-23 2016-Weak-FH-Bisim/WeakBisim.tex
rework proof

For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. By  Definition \ref{def-Weak-bisim} we have for an open transition:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1 \OTarrow {\tau} s'^1} \in \mathcal{T}          
\end{mathpar}
there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. \\
 $\Pred_{s1,t} \land \Pred_i^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s'^1,t_x}\subst{\Post_i^1}\subst{\Post_{OT_x}}\right)$

And similarly, for an open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3 \OTarrow {\tau} s'^3} \in \mathcal{T}          
\end{mathpar}
there exist weak open transition $\symb{WOT}_z^{z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},\Post_{OT_z}}
         {t'' \OTWeakarrow {\alpha_x} t_z}
\end{mathpar}
 such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, (s'^3,t_z|\Pred_{s'^3,t_z})\in \mathcal{R}$. \\
 $\Pred_{s^3,t''} \land \Pred_i^3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{jz}  \Rightarrow \Pred_{OT_z}
     \land \alpha_z\!=\!\tau \land  
     \Pred_{s'^3,t_z}\subst{\Post_i^3}\subst{\Post_{OT_z}}\right)$

Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_y^{y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
         {t' \OTWeakarrow {\alpha_y} t_y}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, (s'^2,t_y|\Pred_{s'^2,t_y})\in \mathcal{R}$; \\
 $\Pred_{s^2,t'} \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
   \left( \forall j\in J_y. \vis{\beta^2_j}=\gamma_{jy}  \Rightarrow \Pred_{OT_y}
     \land \alpha\!=\!\alpha_y \land  
     \Pred_{s'^2,t_y}\subst{\Post^2}\subst{\Post_{OT_y}}\right)$

>>>>

For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.

\paragraph{1st transition}

We have
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s \OTarrow {\tau} s'^1} \in \mathcal{T}          
\end{mathpar}
Also, we have $(s,t|\Pred_{s,t})\in\mathcal{R}$. Then
by  Definition \ref{def-Weak-bisim} we have for an open transition:

there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred_i^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s'^1,t_x}\subst{\Post_i^1}\subst{\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$ and $\alpha_x\!=\!\tau$ we have 
directly\NOTE{the argumet is not trivial!}:
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\paragraph{2nd transition}

Concerning the middle open transition, we have
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s'^1 \OTarrow {\alpha} s'^2} 
\end{mathpar}
For each of the WOTs obtained above, we have the following.
We have $(s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. Then
 by Definition \ref{def-Weak-bisim}:

 there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
         {t_x \OTWeakarrow {\alpha_y} t_{x y}}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, 
(s'^2,t_y|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s^2,t'} \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
   \left( \forall j\in J_y. \vis{\beta^2_j}=\gamma_{jy}  \Rightarrow \Pred_{OT_y}
     \land \alpha\!=\!\alpha_y \land  
     \Pred_{s'^2,t_y}\subst{\Post^2}\subst{\Post_{OT_y}}\right)$

 \paragraph{third  transition}
And similarly, for an open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s'^2 \OTarrow {\tau} s'} \in \mathcal{T}          
\end{mathpar}
Additionally, for each $x$ and $y$, we have 
$(s'^2,t_y|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$
and by Definition \ref{def-Weak-bisim}:

there exist weak open transition $\symb{WOT}_{x y z}^{x,y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},\Post_{OT_z}}
         {t_{x y} \OTWeakarrow {\alpha_x} t_{x y z}}
\end{mathpar}
 such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, 
(s',t_{x y z}|\Pred_{s',t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s'^2,t_{x y}} \land \Pred_i^3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{jz}  \Rightarrow \Pred_{OT_z}
     \land \alpha_z\!=\!\tau \land  
     \Pred_{s'^3,t_z}\subst{\Post_i^3}\subst{\Post_{OT_z}}\right)$
